Appendix

### 2019-07-25 figures/02_hierarchical_demo.Rmd
cleanup

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

gg_lines <- ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme_cowplot() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct)", # , NLCD 2011
         y = "TP (ug/L)")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
    scale_color_manual(values = rep("black", 26))
gg_hu4 <- ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = rep("black", 5))

cowplot::plot_grid(
  plot_grid(nullGrob(), gg_lines, nullGrob(), 
            ncol = 1, rel_heights = c(0.33, 1, 0.33)), 
  gg_hu4)
```

>>>>

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

gg_lines <- ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme_cowplot() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct)", # , NLCD 2011
         y = "TP (ug/L)")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
    scale_color_manual(values = rep("black", 26))

gg_hu4 <- ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
    coord_sf(datum = NA) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = rep("black", 5)) +
  ggtitle("# of lakes per region")

cowplot::plot_grid(
  plot_grid(nullGrob(), gg_lines, nullGrob(), 
            ncol = 1, rel_heights = c(0.52, 1, 0.51)), 
  gg_hu4, rel_widths = c(0.7, 1))
```

### 2019-07-25 figures/07_model-selection.Rmd
cleanup

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty))

text_colors <- ifelse(gg_tp$signif == 0, "black", "red")
(gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  theme(axis.text.y = element_text(size = 12, color = text_colors)) +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) + 
  ggtitle("TP ~ Slope") +
  xlab(""))
```

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tn_fe <- ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) + ggtitle("TN ~ Slope") +
  xlab("") 
```

```{r tn_re_hu4}

# map significant random effects hu4s
gg_hu4 <- ggplot() +
    geom_sf(data = hu4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

@@

```{r fe}
cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
                   gg_tn_fe + theme(axis.text.y = element_blank(), 
                                    axis.title.x = element_blank()), 
                   rel_widths = c(1, 0.6))
```

>>>>

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Land-use cover", "Buffer composition", 
                                      "Lake")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer composition")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

gp <- ggplotGrob(gg_tp_fe)
facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
                function(l) length(l$range$range))
gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
gg_tp_fe <- ggplotify::as.ggplot(gp)
gg_tp_fe
```

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Land-use cover", "Buffer composition", 
                                      "Lake")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer composition")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tn_fe <- 
  ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = c(-0.6, 1.6)) +
  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = 0.44, vjust = 0.5, hjust = "left") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TN") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent"), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

gp <- ggplotGrob(gg_tn_fe)
facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
x.var         <- sapply(ggplot_build(gg_tn_fe)$layout$panel_scales_x,
                function(l) length(l$range$range))
gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
gg_tn_fe <- ggplotify::as.ggplot(gp)
gg_tn_fe
```

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}

# map significant random effects hu4s
gg_hu4 <- ggplot() +
    geom_sf(data = hu4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    coord_sf(datum = NA) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

@@

```{r fe}
cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
                   gg_tn_fe + theme(axis.text.y = element_blank(), 
                                    axis.title.x = element_blank()), 
                   rel_widths = c(1, 1))
```

### 2019-07-25 manuscript/appendix.Rmd
cleanup

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
# waffle
library(waffle)
library(hrbrthemes)

dt_waffle <- tidyr::gather(dt, key = "key", value = "value", -`Trophic State`) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "All Lakes", `value` = 2) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
  arrange(`Trophic State`) %>%
  dplyr::filter(key == "This Study")

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))

>>>>

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
# waffle
library(waffle)

total_cells <- 41.5
dt_waffle <- dt %>% 
  dplyr::rename(trophic_state = `Trophic State`) %>%
  tidyr::gather(key = "key", value = "value", -trophic_state) %>%
  dplyr::filter(key == "This Study") %>%
  mutate(value = floor((value / 100) * total_cells)) %>%
  arrange(trophic_state)
# sum(dt_waffle$value)
# add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%

ggplot(dt_waffle,
       aes(fill = trophic_state, values = value)) +
  geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 1))
